\documentclass[11pt,a4paper,sans]{moderncv}        

\moderncvstyle{banking}                             
\moderncvcolor{blue}                              

\usepackage[scale=0.9]{geometry}

\name{Joseff}{Thomas}
\address{Sheffield}                 
\email{joseffthomas91@gmail.com}                             
\homepage{www.jthom.me}                       
\social[linkedin]{josefft}                        
\social[twitter]{josefft}                          
\social[github]{josefft91}                              

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}

%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Skills}
\begin{minipage}[t]{0.45\textwidth}
	\textbf{Frontend:}
	\begin{itemize}
		\item Experience with JavaScript, Vue.js, React and jQuery.
		\item Proficient at hand coding HTML and CSS/SASS to web standards.
		\item Experience with frontend frameworks such as Bootstrap, UIKit and Tailwind CSS.
		\item Knowledge of responsive design, accessibility and cross-browser compliance.
		\item Familiar with Webpack.
	\end{itemize}
\end{minipage}
\begin{minipage}[t]{0.45\textwidth}
	\textbf{Backend:}
	\begin{itemize}
		\item Professional experience with PHP, CodeIgniter and Symfony. 
		\item Knowledge of object-orientated design, MVC architecture and database design.
		\item Experience with writing SQL for MySQL and using ORM tools such as ActiveRecord and Propel.
		\item Knowledge of interacting with RESTful APIs.
		\item Familiar with Java, Ruby and Python.
		\item Familiar with unit testing and TDD.
		\item Familiar with Composer.
	\end{itemize}
\end{minipage}
\\\\
\textbf{Other Relevant Skills}
\begin{itemize}
	\item Knowledge of source control and have experience with Git.
	\item Knowledge in deploying development environments using Vagrant.
	%\item Familiar with Gulp.
	%\item Basic experience of installing and configuring both Windows and Linux servers.
	\item Quick and keen learner, like to keep skills relevant and up to date by self teaching, reading blogs and attending conferences.  
\end{itemize}


\section{Experience}

\cventry{May 2018--Present}{Web Developer}{Freelance}{Remote/Sheffield}{}{\href{www.jthom.me}{www.jthom.me} \newline{}%
I have been working with several organisations on a freelance basis. }
\begin{small}
\textbf{Peak Climbing Club (2018--2019)}\\
\href{http://www.peakclimbingclub.co.uk}{www.peakclimbingclub.co.uk}
\begin{itemize}%
\item Developed the new Peak Climbing Club website (\href{http://www.peakclimbingclub.co.uk}{www.peakclimbingclub.co.uk}) using Bootstrap and Processwire. 
\end{itemize}
\textbf{Peter and Paul (2018)}
\begin{itemize}
\item Peter and Paul are a brand design agency, I worked with them on a short contract building websites using ProcessWire, Tailwind CSS and UIKit.
\item Involved in the development of \href{http://www.eizocolour.com}{www.eizocolour.com}. My major contributions were the Spotlight, Student Award and Support pages. 
\end{itemize}

\textbf{Nahuru (2018)}\\
\href{http://www.nahuru.com}{www.nahuru.com}
\begin{itemize}%
\item Nahuru is a data analytics company, which focuses on audience measurement services for the entertainment and marketing industry.
\item Developed their redesigned website (\href{http://www.nahuru.com}{www.nahuru.com}) using PyroCMS and Bootstrap.
\item Nahuhash - developed a search user interface using Vue.js to interact with their `Search Automation (Sauto)' backend system. \\
%\item Developed a dashboard user interface to display Periscope Data charts. \\
\end{itemize}

\end{small}

\cventry{November 2017--May 2018}{Symfony PHP Developer}{Tonic Works}{Sheffield}{}{\href{www.tonic.works}{www.tonic.works} \newline{}%
My role at Tonic Works has involved working on various SaaS projects within the Legal Tech sector using Symfony and React. }
\textbf{Responsibilities and Achievements:}%
\begin{itemize}%
\item Furthering the development of "QuoteXpress" CRM system using Symfony and React.
\item Building a PHP API wrapper for the Land Registry SOAP API. \\
\end{itemize}%
\newpage
\cventry{November 2016--November 2017}{Web Developer}{Twinkl Educational Publishing}{Sheffield}{}{\href{www.twinkl.co.uk}{www.twinkl.co.uk} \newline{}%
Twinkl is an online educational resource company with over two million registered users worldwide. My role has involved furthering the development of the Twinkl website and internal systems using PHP and MySQL. }
\textbf{Responsibilities and Achievements:}%
\begin{itemize}%
\item Built a help desk ticketing system in order to bring customer support into one place. A part of this made use of the the Gmail API to send and receive emails via the help desk.
\item Used the Paypal API to build system to allow colleagues to send payment requests to users and also make refunds through the system.
\item Modernised processes in the web team such as using Composer, using Xdebug and switching to PHPStorm.  \\  
\end{itemize}%
%\newpage
\cventry{July 2014--November 2016}{Web Developer}{ToucanTech}{London}{}{\href{www.toucantech.com}{www.toucantech.com} \newline{}% 
ToucanTech is community management software for institutions such as schools and universities. It is composed of 
two major sections, a front end community network portal and an admin portal, which includes a user database, CRM, email engine, CMS and 
fundraising tools. }
\textbf{Responsibilities and Achievements:}%
\begin{itemize}%
\item My role involves working closely with the founders and CTO to develop new features and functionality using PHP, CodeIgniter and MySQL.
\item Some key features that I have developed have included:
	\begin{itemize}%
		\item Photo gallery module, which allows users to upload and view photos on the network. 
		\item Activity tracker module, which allows school administrators to keep of a log of activities with end users.
		\item Various enhancements and bug fixes to keep the networks running smoothly.
	\end{itemize}
%\item Occasional non development tasks such as setting up new clients and exhibiting at conferences. 
\item Recruiting and training new junior developers.\\
\end{itemize}

\cventry{September 2013--September 2015}{Web Developer}{BusinessBecause}{London}{}
{\href{www.businessbecause.com}{www.businessbecause.com} \newline{}%
My role involved furthering the development of the niche networking website, BusinessBecause, a global network for MBA students. The website is built in PHP/CodeIgniter, incorporating modules from PyroCMS.} 
\textbf{Responsibilities and Achievements:}%
\begin{itemize}%
\item Created new features and functionality using PHP, CodeIgniter and MySQL as well as updating the front end using HTML5, CSS3 and JavaScript. 
\item Simplified the registration process, which allowed people to register using their LinkedIn and/or Facebook accounts.
\item Optimised the website for mobile, using HTML5, CSS3 and Bootstrap, which led to an increase in traffic from mobile users.\\
\end{itemize}

\cventry{June 2011--September 2012}{Software Developer (Industrial Placement)}{Compliance Control Ltd}{Northwich}{}
{This was an industrial placement as part of my degree. I was involved in developing "ComplianceControl Centre", an electronic document and quality management system for use in the pharmaceutical and life sciences industries. This was written using PHP and an Oracle database. Also included building the front end using standards compliant XHTML, CSS and JavaScript \newline}


\cventry{June 2010--September 2010}{IT Technical Support Assistant}{The Shrewsbury and Telford Hospital NHS Trust}{Shrewsbury}{}
{This was a general IT support role, my main duty was replacing and configuring old computers throughout the hospital. In addition, I was also responsible for fixing day to day IT problems for end users.}

\section{Education}
\cventry{2009--2013}{BSc (Hons) Computer Science}{Aberystwyth University}{}{}{}
\cventry{2007--2009}{A-Levels}{The Thomas Adams Sixth Form}{}{}{History, IT, Geography}
\cventry{2002--2007}{GCSEs}{The Thomas Adams School}{}{}{10 including English and Maths}

\section{Interests}
My interests include rock climbing, photography, running, cycling and cooking.
%\begin{itemize}
	%\item Rock climbing - I am a keen climber and help run a climbing meetup group, organising meets at climbing walls and trips away.
	%\item Photography - I enjoy street photography and a selection of my photos can be viewed on my flickr - \href{https://www.flickr.com/photos/josefft/}{https://www.flickr.com/photos/josefft/}.
	%\item My other interests include running, cycling and cooking.
%\end{itemize}

\end{document}
